---
title: "RADS Metadata Analysis"
author: "Alicia Hofelich Mohr"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = '..')
```


# Data Collection Methods

### Data by Affiliation 
Datacite metadata were pulled using the `rdatacite` package in November 2022. Each of the six institutions were searched using the name of each University in the `creators.affiliation.name` metadata field. Results were filtered to include DOIs with a `publicationYear` of 2012 or later, and a `resourceTypeGeneral` of dataset or software. As the search terms returned other institutions with similar names, results were filtered to include DOIs only from the relevant institutional affiliations. 

Following recommendations of the Crossref API, metadata was pulled from the April 2022 Public Release file (http://dx.doi.org/10.13003/83b2gq). DOIs were searched records with a `created-dateparts` year of 2012 or newer, that had a `type` of datasets (Crossref does not have software as an available type), and had an author affiliation with one of the six institutions. 

## Instituional repositories
Upon initial examination of the affiliation data, we realized that our own institutional repositories were not represented in the data because the affiliation metadata field was not completed as part of the DOI generation process. 

To pull data shared in our institutional repositories as a comparison, a second search was performed to retrieve DOIs published by the insitutional repositories at each university. For the insitutional repositories using DataCite to issue DOIs (5 out of the 6 institutions at the time), the datacite API queried by names of the institutional repositories in the `publisher` metadata field. For the one institution using CrossRef to issue DOIs (Duke), the crossref API was used to retrieve all DOIs published using the Duke member prefixes.  

Institutional repository data was then filtered to include only the relevant repositories, datasets and software resource types, and DOIs published in 2012 or later. 

Affiliation data from datacite, affiliation data from cross ref, and the institutional repository data were combined into a single dataset. 




# Analysis

Load required packages and read in combined data. 
```{r}
#packages
pacman::p_load(dplyr, 
               tidyr, 
               ggplot2, 
               rjson,
               rdatacite,
               cowplot, 
               stringr, 
               knitr, 
               DT)



#Load the combined data from 3_Combined_data.R
load(file="data_rdata_files/Combined_ALL_data.Rdata")

#rename object
all_dois <- combined_dois 

#re-factor group so that datacite appears before cross ref
all_dois$group <- factor(all_dois$group, levels = c("Affiliation - Datacite", "Affiliation - CrossRef", "IR_publisher"))
```

# Collapse DOIs by container 

Some repositories (such as Harvard's Dataverse and Qualitative Data Repository) assign DOIs at the level of the file, rather than the study. Similarly, Zenodo often has many related DOIs for multiple figures within a study. In order to attempt to compare study-to-study counts of data sharing, look at the DOIs collapsed by "container".  
```{r}
by_container <- 
all_dois %>% 
  filter(!is.na(container_identifier)) %>% 
  group_by(container_identifier, publisher, title, institution) %>% 
  summarize(count=n()) %>% 
  arrange(desc(count))
```

How many publishers have container DOIs?
```{r}
by_container %>% 
  group_by(publisher) %>% 
  summarize(count=n()) %>% 
  arrange(desc(count)) %>% 
  datatable

```


Collapsing by container for counts
```{r}
containerdups <- which(!is.na(all_dois$container_identifier) & duplicated(all_dois$container_identifier))

all_dois_collapsed <- all_dois[-containerdups,]
```

This leaves a total of `r nrow(all_dois_collapsed)` cases. 



# Overview of the data

DOI types by resource
```{r}
all_dois_collapsed %>% 
  group_by(resourceTypeGeneral, group) %>% 
  summarize(count=n()) %>% 
  pivot_wider(names_from = group, 
              values_from = count, 
              values_fill = 0) %>% 
  kable()
```


DOI by institutional affiliation/publisher
```{r}
all_dois_collapsed %>% 
  group_by(group, institution) %>% 
  summarize(count=n()) %>% 
  pivot_wider(names_from = group,
              values_from = count) %>% 
  kable()
```


## Collapse IRs into a single category

Look at all the Institutional Repositories Captured
```{r}
IR_pubs <- all_dois_collapsed %>% 
  filter(group == "IR_publisher") %>% 
  group_by(publisher_plus) %>% 
  summarize(count = n()) 

IR_pubs %>% 
  kable(col.names = c("Institutional Repository", "Count"))

```

Replace all of these publishers with "Institutional Repository" so that they will be represented in a single bar.
```{r}
all_dois_collapsed$publisher[which(all_dois_collapsed$publisher_plus %in% unique(IR_pubs$publisher_plus))] <- "Institutional Repository"

#catch the rest of the "Cornell University Library"
all_dois_collapsed$publisher[which(all_dois_collapsed$publisher == "Cornell University Library")] <- "Institutional Repository"

#and stray VT
all_dois_collapsed$publisher[which(all_dois_collapsed$publisher == "University Libraries, Virginia Tech")] <- "Institutional Repository"

#and DRUM
all_dois_collapsed$publisher[which(all_dois_collapsed$publisher == "Data Repository for the University of Minnesota (DRUM)")] <- "Institutional Repository"

##ICPSR is also inconsistent
all_dois_collapsed$publisher[grep("Consortium for Political", all_dois_collapsed$publisher)] <- "ICPSR"


```


## Overall Count of Data and Software DOIs

Think we just keep these together for the main analysis...

```{r}
by_publisher_collapse <- all_dois_collapsed %>% 
  group_by(publisher, institution) %>% 
  summarize(count=n()) %>% 
  arrange(institution, desc(count))
```

Table of publisher counts
```{r}
by_publisher_collapse_table <- by_publisher_collapse %>% 
  pivot_wider(names_from = institution, 
              values_from = count, 
              values_fill = 0) %>% 
  rowwise %>% 
  mutate(Total = sum(c_across(Cornell:`Washington U`))) %>% 
  arrange(desc(Total))

by_publisher_collapse_table %>% 
  datatable
```


Write out the table of data & software publishers
```{r}
write.csv(by_publisher_collapse_table, file="data_summary_data/Counts of  Publishers By Insitituion - Collapsed by container.csv", row.names = F)
```


## Graphs


### Top 8 publishers of data dois

```{r}
by_publisher_dc_collapse <- all_dois_collapsed %>% 
  group_by(publisher, institution) %>% 
  summarize(count=n()) %>% 
  arrange(institution, desc(count))

#table of  publishers - data
by_publisher_dc_collapse_table <- by_publisher_dc_collapse %>% 
  pivot_wider(names_from = institution, 
              values_from = count, 
              values_fill = 0) %>% 
  rowwise %>% 
  mutate(Total = sum(c_across(Cornell:`Washington U`))) %>% 
  arrange(desc(Total))
```

Look at publishers based on rank of number of DOIs
```{r}
by_publisher_dc_collapse_table %>% 
  group_by(publisher) %>% 
  summarize(count=sum(Total)) %>% 
  arrange(desc(count)) %>% 
  mutate(pubrank = order(count, decreasing = T)) %>% 
  ggplot(aes(x=pubrank, y=count)) +
  geom_bar(stat="identity") +
  scale_x_continuous(limits = c(0,25)) +
  labs(x = "Publisher Rank", y="Number of DOIs", title="Number of DOIs by top Publishers")+
  theme_bw() 
```

Look at the top 8 publishers - how many does this capture?
```{r}
top8pubs <- by_publisher_dc_collapse_table$publisher[1:8]

by_publisher_dc_collapse_table %>% 
  group_by(publisher) %>% 
  summarize(count=sum(Total)) %>% 
  mutate(intop8pub = publisher %in% top8pubs) %>% 
  group_by(intop8pub) %>% 
  summarize(totalDOIs = sum(count), nrepos = n()) %>% 
  ungroup() %>% 
  mutate(propDOIs = totalDOIs/sum(totalDOIs))
```


```{r}
top8colors <- c("Harvard Dataverse" = "dodgerblue2",
                "Zenodo" = "darkorange1",
                "ICPSR" = "darkcyan",
                "Dryad" = "lightgray", 
                "figshare" = "purple", 
                "Institutional Repository" = "lightblue", 
                "ENCODE Data Coordination Center" = "gold2", 
                "Faculty Opinions Ltd" = "darkgreen")



(by_publisher_plot_collapse <-  by_publisher_dc_collapse %>% 
    filter(publisher %in% top8pubs) %>% 
    ggplot(aes(x=institution, y=count, fill=publisher)) +
    geom_bar(stat="identity", position=position_dodge(preserve = "single")) +
    scale_fill_manual(values = top8colors, name="Publisher")+
    guides(fill = guide_legend(title.position = "top")) +
    scale_y_continuous(breaks = seq(from = 0, to=5000, by=500)) +
    coord_cartesian(ylim = c(0,5000)) +
    labs(x = "Institution", y="Count of Collapsed DOIs", caption = "Note: Michigan ENCODE bar cut off for scaling") +
    theme_bw() +
    theme(legend.position = "bottom", legend.title.align = .5))


ggsave(by_publisher_plot_collapse, filename = "figures/Counts of DOIs by Institution_DOIcollapsed.png", device = "png",  width = 8, height = 6, units="in")
```


### Institutional Graphs - Collapsed {.tabset .tabset-fade .tabset-pills}

#### Cornell

```{r, echo=FALSE}
by_publisher_dc_collapse %>% 
  ungroup() %>% 
  filter(institution == "Cornell") %>% 
  arrange(desc(count)) %>% 
  slice_head(n=8) %>% 
  ggplot(aes(x=publisher, y=count, fill=publisher)) +
    geom_bar(stat="identity", position=position_dodge(preserve = "single")) +
    scale_fill_manual(values = top8colors, name="Publisher")+
    guides(fill = guide_legend(title.position = "top")) +
    labs(y="Count of Data DOIs - Collapsed", title = "Cornell Top 8 Data Publishers") +
    coord_flip() +
    theme_bw() +
    theme(legend.position = "bottom", legend.title.align = .5)
```

```{r, echo=F}
i = "Cornell"
all_dois_collapsed %>% 
   filter(institution == i) %>% 
   group_by(publicationYear, resourceTypeGeneral) %>% 
   summarize(count=n()) %>% 
   mutate(publicationYear = factor(publicationYear)) %>% 
   ggplot(aes(x=publicationYear, y=count, group=resourceTypeGeneral)) +
   geom_line(stat = "identity", aes(color=resourceTypeGeneral)) +
   scale_color_discrete( name = "Resource Type") +
   labs(x="Year", y="Number of DOIs", title=paste(i, "Number of Shared DOIs (2012-2022)"))+
   theme_bw()
```

#### Duke

```{r, echo=FALSE}
by_publisher_dc_collapse %>% 
  ungroup() %>% 
  filter(institution == "Duke") %>% 
  arrange(desc(count)) %>% 
  slice_head(n=8) %>% 
  ggplot(aes(x=publisher, y=count, fill=publisher)) +
    geom_bar(stat="identity", position=position_dodge(preserve = "single")) +
    scale_fill_manual(values = top8colors, name="Publisher")+
    guides(fill = guide_legend(title.position = "top")) +
    labs(y="Count of Data DOIs - Collapsed", title = "Duke Top 8 Data Publishers") +
    coord_flip() +
    theme_bw() +
    theme(legend.position = "bottom", legend.title.align = .5)
```

```{r, echo=F}
i = "Duke"
all_dois_collapsed %>% 
   filter(institution == i) %>% 
   mutate(publicationYear = factor(gsub("-", "", publicationYear))) %>%
   group_by(publicationYear, resourceTypeGeneral) %>% 
   summarize(count=n()) %>% 
   ggplot(aes(x=publicationYear, y=count, group=resourceTypeGeneral)) +
   geom_line(stat = "identity", aes(color=resourceTypeGeneral)) +
   scale_color_discrete( name = "Resource Type") +
   labs(x="Year", y="Number of DOIs", title=paste(i, "Number of Shared DOIs (2012-2022)"))+
   theme_bw()
```

#### Michigan

```{r, echo=FALSE}
by_publisher_dc_collapse %>% 
  ungroup() %>% 
  filter(institution == "Michigan") %>% 
  arrange(desc(count)) %>% 
  slice_head(n=8) %>% 
  ggplot(aes(x=publisher, y=count, fill=publisher)) +
    geom_bar(stat="identity", position=position_dodge(preserve = "single")) +
    scale_fill_manual(values = top8colors, name="Publisher")+
    guides(fill = guide_legend(title.position = "top")) +
    labs(y="Count of Data DOIs - Collapsed", title = "Michigan Top 8 Data Publishers") +
    coord_flip() +
    theme_bw() +
    theme(legend.position = "bottom", legend.title.align = .5)
```

```{r, echo=F}
i = "Michigan"
all_dois_collapsed %>% 
   filter(institution == i) %>% 
   group_by(publicationYear, resourceTypeGeneral) %>% 
   summarize(count=n()) %>% 
   mutate(publicationYear = factor(publicationYear)) %>% 
   ggplot(aes(x=publicationYear, y=count, group=resourceTypeGeneral)) +
   geom_line(stat = "identity", aes(color=resourceTypeGeneral)) +
   scale_color_discrete( name = "Resource Type") +
  coord_cartesian(ylim=c(0,5000)) +
   labs(x="Year", y="Number of DOIs", title=paste(i, "Number of Shared DOIs (2012-2022)"), caption = "Note: 2021 bar cut off for scaling (ENCODE)")+
   theme_bw()
```

#### Minnesota

```{r, echo=FALSE}
by_publisher_dc_collapse %>% 
  ungroup() %>% 
  filter(institution == "Minnesota") %>% 
  arrange(desc(count)) %>% 
  slice_head(n=8) %>% 
  ggplot(aes(x=publisher, y=count, fill=publisher)) +
    geom_bar(stat="identity", position=position_dodge(preserve = "single")) +
    scale_fill_manual(values = top8colors, name="Publisher")+
    guides(fill = guide_legend(title.position = "top")) +
    labs(y="Count of Data DOIs - Collapsed", title = "Minnesota Top 8 Data Publishers") +
    coord_flip() +
    theme_bw() +
    theme(legend.position = "bottom", legend.title.align = .5)
```

```{r, echo=F}
i = "Minnesota"
all_dois_collapsed %>% 
   # filter(resourceTypeGeneral == "Dataset" | resourceTypeGeneral == "Software") %>% 
   # filter(publisher != "ENCODE Data Coordination Center", 
   #       publisher != "Faculty Opinions Ltd")  %>% 
   filter(institution == i) %>% 
   group_by(publicationYear, resourceTypeGeneral) %>% 
   summarize(count=n()) %>% 
   mutate(publicationYear = factor(publicationYear)) %>% 
   ggplot(aes(x=publicationYear, y=count, group=resourceTypeGeneral)) +
   geom_line(stat = "identity", aes(color=resourceTypeGeneral)) +
   scale_color_discrete( name = "Resource Type") +
   labs(x="Year", y="Number of DOIs", title=paste(i, "Number of Shared DOIs (2012-2022)"))+
   theme_bw()
```

#### Virginia Tech

```{r, echo=FALSE}
by_publisher_dc_collapse %>% 
  ungroup() %>% 
  filter(institution == "Virginia Tech") %>% 
  arrange(desc(count)) %>% 
  slice_head(n=8) %>% 
  ggplot(aes(x=publisher, y=count, fill=publisher)) +
    geom_bar(stat="identity", position=position_dodge(preserve = "single")) +
    scale_fill_manual(values = top8colors, name="Publisher")+
    guides(fill = guide_legend(title.position = "top")) +
    labs(y="Count of Data DOIs - Collapsed", title = "Virginia Tech Top 8 Data Publishers") +
    coord_flip() +
    theme_bw() +
    theme(legend.position = "bottom", legend.title.align = .5)
```

```{r, echo=F}
i = "Virginia Tech"
all_dois_collapsed %>% 
   # filter(resourceTypeGeneral == "Dataset" | resourceTypeGeneral == "Software") %>% 
   # filter(publisher != "ENCODE Data Coordination Center", 
   #       publisher != "Faculty Opinions Ltd")  %>% 
   filter(institution == i) %>% 
   group_by(publicationYear, resourceTypeGeneral) %>% 
   summarize(count=n()) %>% 
   mutate(publicationYear = factor(publicationYear)) %>% 
   ggplot(aes(x=publicationYear, y=count, group=resourceTypeGeneral)) +
   geom_line(stat = "identity", aes(color=resourceTypeGeneral)) +
   scale_color_discrete( name = "Resource Type") +
   labs(x="Year", y="Number of DOIs", title=paste(i, "Number of Shared DOIs (2012-2022)"))+
   theme_bw()
```

#### Wash U

```{r, echo=FALSE}
by_publisher_dc_collapse %>% 
  ungroup() %>% 
  filter(institution == "Washington U") %>% 
  arrange(desc(count)) %>% 
  slice_head(n=8) %>% 
  ggplot(aes(x=publisher, y=count, fill=publisher)) +
    geom_bar(stat="identity", position=position_dodge(preserve = "single")) +
    scale_fill_manual(values = top8colors, name="Publisher")+
    guides(fill = guide_legend(title.position = "top")) +
    labs(y="Count of Data DOIs - Collapsed", title = "Wash U Top 8 Data Publishers") +
    coord_flip() +
    theme_bw() +
    theme(legend.position = "bottom", legend.title.align = .5)
```

```{r, echo=F}
i = "Washington U"
all_dois_collapsed %>% 
   # filter(resourceTypeGeneral == "Dataset" | resourceTypeGeneral == "Software") %>% 
   # filter(publisher != "ENCODE Data Coordination Center", 
   #       publisher != "Faculty Opinions Ltd")  %>% 
   filter(institution == i) %>% 
   group_by(publicationYear, resourceTypeGeneral) %>% 
   summarize(count=n()) %>% 
   mutate(publicationYear = factor(publicationYear)) %>% 
   ggplot(aes(x=publicationYear, y=count, group=resourceTypeGeneral)) +
   geom_line(stat = "identity", aes(color=resourceTypeGeneral)) +
   scale_color_discrete( name = "Resource Type") +
   labs(x="Year", y="Number of DOIs", title=paste(i, "Number of Shared DOIs (2012-2022)"))+
   theme_bw()
```

# Repository Poliferation by Year

How many different publishers are researchers sharing their data and how does this change over time?

```{r}
by_year_nrepos <- all_dois_collapsed %>% 
  group_by(publicationYear, publisher, institution) %>% 
  summarize(nDOIs = n()) %>% 
  group_by(publicationYear, institution) %>% 
  summarize(npublishers = n(), totalDOIs = sum(nDOIs))

by_year_nrepos %>% 
  ggplot(aes(x=publicationYear, y=npublishers, group=institution)) +
  geom_line(aes(color=institution)) +
  labs(x="Year", 
       y="Number of Repositories", 
       title="Number of Repositories Where Data and Software are Shared Across Time") +
  theme_bw() +
  theme(legend.title = element_blank())

```


# Further collapse by Version

We can also look at the data collapsed by version of a record. This was motivated because some repositories have multiple entries for the different versions of the same dataset/collection. And some entries have many versions. 

Explore versions

Some Repositories attach "vX" to the doi. 
```{r}
all_dois_collapsed <- all_dois_collapsed %>% 
  mutate(hasversion = grepl("\\.v[[:digit:]]+$", DOI))


all_dois_collapsed %>% 
  filter(hasversion == TRUE) %>% 
  group_by(publisher, hasversion) %>% 
  summarize(count=n()) %>% 
  arrange(desc(count)) %>% 
  datatable()

```

Some repositories use the "VersionCount" 
```{r}
all_dois_collapsed %>% 
  filter(versionCount > 0) %>% 
  group_by(publisher) %>% 
  summarize(count=n(), AvgNversions = round(mean(versionCount),2)) %>% 
  arrange(desc(count)) %>% 
  datatable()
```

Some use "metadataVersion"
```{r}
all_dois_collapsed %>% 
  filter(metadataVersion > 0) %>% 
  group_by(publisher) %>% 
  summarize(count=n(), AvgNversions = round(mean(metadataVersion),2)) %>% 
  arrange(desc(count)) %>% 
  datatable()
```


How to collapse by version? Maybe that's for another day... 


# Completeness? 


# Write out institutional data

Write out CSV files for each institution: 

* All DOIs
* All DOIs collapsed

```{r, eval=FALSE}
for (i in unique(all_dois$institution)) {
  all_dois %>% 
    filter(institution == i) %>% 
    write.csv(file=paste0("data_all_dois/All_dois_", i, gsub("-", "", Sys.Date()), ".csv"), row.names = F)
  
  all_dois_collapsed %>% 
    filter(institution == i) %>% 
    write.csv(file=paste0("data_all_dois/All_dois_collapsed_", i, gsub("-", "", Sys.Date()), ".csv"), row.names = F)
}
```




<!-- ## Overall counts by resource type -->

<!-- Counts by resource type -->
<!-- ```{r} -->
<!-- by_resource <- all_dois %>%  -->
<!--   group_by(institution, resourceTypeGeneral) %>%  -->
<!--   summarize(count=n()) %>%  -->
<!--   arrange(institution, desc(count))  -->
<!-- ``` -->

<!-- Create a table of top resources -->
<!-- ```{r} -->
<!-- by_resource_table <-  by_resource %>%  -->
<!--   #filter(resourceTypeGeneral %in% c("Dataset", "Software", "Text", "Image")) %>%  -->
<!--   pivot_wider(names_from = institution,  -->
<!--               values_from = count,  -->
<!--               values_fill = 0) %>%   -->
<!--   rowwise %>%  -->
<!--   mutate(Total = sum(c_across(Cornell:`Washington U`))) %>%  -->
<!--   arrange(desc(Total)) -->

<!-- by_resource_table %>%  -->
<!--   datatable -->
<!-- ``` -->

<!-- Write out the resources -->
<!-- ```{r} -->
<!-- write.csv(by_resource_table, file = "data_summary_data/Counts of Resource Types by Insitution.csv", row.names = F) -->
<!-- ``` -->

<!-- ## Data specific DOIs -->

<!-- Subset to only datasets -->
<!-- ```{r} -->
<!-- data_dois <- all_dois %>%  -->
<!--   filter(resourceTypeGeneral == "Dataset")  -->
<!-- ``` -->

<!-- Data DOIs by publisher -->
<!-- ```{r} -->
<!-- by_publisher_data <- data_dois %>%  -->
<!--   group_by(publisher, institution) %>%  -->
<!--   summarize(count=n()) %>%  -->
<!--   arrange(institution, desc(count)) -->


<!-- by_publisher_data_table <- by_publisher_data %>%  -->
<!--   pivot_wider(names_from = institution,  -->
<!--               values_from = count,  -->
<!--               values_fill = 0) %>%  -->
<!--   rowwise %>%  -->
<!--   mutate(Total = sum(c_across(Cornell:`Washington U`))) %>%  -->
<!--   arrange(desc(Total)) -->

<!-- by_publisher_data_table %>%  -->
<!--   datatable() -->

<!-- ``` -->

<!-- Write out the table of data publishers -->
<!-- ```{r} -->
<!-- write.csv(by_publisher_data_table, file="data_summary_data/Counts of Data Publishers By Insitituion.csv", row.names = F) -->
<!-- ``` -->

<!-- After reviewing the repositories, we will remove the Faculty Opinions LTD records (these are reviews of articles, no data attached) and the ENCODE Data Coordination Center (extreme outlier for Michigan in 2022, unclear what the level of DOI assignment is) from further analysis.  -->

<!-- ## Software specific DOIs -->

<!-- Subset to only software (only datacite has software) -->
<!-- ```{r} -->
<!-- software_dois <- all_dois %>%  -->
<!--   filter(resourceTypeGeneral == "Software") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- by_publisher_software <- software_dois %>%  -->
<!--   group_by(publisher, institution) %>%  -->
<!--   summarize(count=n()) %>%  -->
<!--   arrange(institution, desc(count)) -->

<!-- by_publisher_software_table <- by_publisher_software %>%  -->
<!--   pivot_wider(names_from = institution,  -->
<!--               values_from = count,  -->
<!--               values_fill = 0) %>%  -->
<!--   rowwise %>%  -->
<!--   mutate(Total = sum(c_across(Cornell:`Washington U`))) %>%  -->
<!--   arrange(desc(Total)) -->

<!-- by_publisher_software_table %>%  -->
<!--   datatable -->
<!-- ``` -->


<!-- Write out the table of software publishers -->
<!-- ```{r} -->
<!-- write.csv(by_publisher_software_table, file="data_summary_data/Counts of Software Publishers By Insitituion.csv", row.names = F) -->
<!-- ``` -->

<!-- ## Graphs  -->

<!-- ### Top publishers - Data DOIs -->

<!-- Plot publishers by rank, ordered from most DOIs to least (take top 20). Remove Encode and Faculty opinions LTD from the list.  -->
<!-- ```{r} -->
<!-- by_publisher_data <- by_publisher_data %>%  -->
<!--    filter(publisher != "ENCODE Data Coordination Center",  -->
<!--          publisher != "Faculty Opinions Ltd")  -->

<!-- by_publisher_data_table <- by_publisher_data_table %>%  -->
<!--   filter(publisher != "ENCODE Data Coordination Center",  -->
<!--          publisher != "Faculty Opinions Ltd")  -->

<!-- by_publisher_data %>%  -->
<!--   group_by(publisher) %>%  -->
<!--   summarize(count=sum(count)) %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   mutate(pubrank = order(count, decreasing = T)) %>%  -->
<!--   ggplot(aes(x=pubrank, y=count)) + -->
<!--   geom_bar(stat="identity") + -->
<!--   scale_x_continuous(limits = c(0,20), n.breaks = 20) + -->
<!--   labs(x = "Publisher Rank", y="Number of DOIs", title="Number of DOIs by top Publishers")+ -->
<!--   coord_cartesian(xlim = c(1,20)) + -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- Based on the graph above, it appears that there is a large drop off after the Top 8 publishers. If we look at the Top 8 publishers for the data dois, how many DOIs does this cover? -->
<!-- ```{r} -->
<!-- top7pubs <- by_publisher_data_table$publisher[1:7] -->

<!-- by_publisher_data %>%  -->
<!--   group_by(publisher) %>%  -->
<!--   summarize(count=sum(count)) %>%  -->
<!--   mutate(intop7pub = publisher %in% top7pubs) %>%  -->
<!--   group_by(intop7pub) %>%  -->
<!--   summarize(totalDOIs = sum(count), nrepos = n()) %>%  -->
<!--   ungroup() %>%  -->
<!--   mutate(propDOIs = totalDOIs/sum(totalDOIs)) %>%  -->
<!--   kable(col.names =  c("In Top 8 Publishers", "Total N DOIs", "Total N Publishers", "Proportion of Total DOIs")) -->
<!-- ``` -->

<!-- Plotting Number of DOIs in the top 8 publishers by institution -->
<!-- ```{r, fig.width=11} -->
<!-- top8colors <- c("Harvard Dataverse" = "dodgerblue2", -->
<!--                 "Zenodo" = "darkorange1", -->
<!--                 "ICPSR" = "darkcyan", -->
<!--                 "Dryad" = "lightgray",  -->
<!--                 "Qualitative Data Repository" = "gold1", -->
<!--                 "figshare" = "purple",  -->
<!--                 "Institutional Repository" = "lightblue") -->


<!-- (by_publisher_data_plot <-  by_publisher_data %>%  -->
<!--     filter(publisher %in% top7pubs) %>%  -->
<!--     ggplot(aes(x=institution, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top8colors, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     scale_y_continuous(breaks = seq(from = 0, to=5000, by=500)) + -->
<!--     coord_cartesian(ylim = c(0,5000)) + -->
<!--     labs(x = "Institution", y="Count of Data DOIs", caption = "Note: Michigan Dataverse bar cutoff for scaling") + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5)) -->


<!-- ggsave(by_publisher_data_plot, filename = "figures/Counts of Data DOIs by Institution - ForPaper.png", device = "png",  width = 8, height = 6, units="in") -->
<!-- ``` -->


<!-- ### Institutional Graphs {.tabset .tabset-fade .tabset-pills} -->


<!-- #### Cornell -->

<!-- ```{r, echo=FALSE} -->
<!-- by_publisher_data %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(institution == "Cornell") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=8) %>%  -->
<!--   ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top8colors, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(y="Count of Data DOIs", title = "Cornell Top 8 Data Publishers") + -->
<!--     coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- #### Duke -->
<!-- ```{r, echo=FALSE} -->
<!-- by_publisher_data %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(institution == "Duke") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=8) %>%  -->
<!--   ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top8colors, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(y="Count of Data DOIs", title = "Duke Top 8 Data Publishers") + -->
<!--     coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- #### Michigan -->

<!-- ```{r, echo=FALSE} -->
<!-- by_publisher_data %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(institution == "Michigan") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=8) %>%  -->
<!--   ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top8colors, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(y="Count of Data DOIs", title = "Michigan Top 8 Data Publishers") + -->
<!--     coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- #### Minnesota -->

<!-- ```{r, echo=FALSE} -->
<!-- by_publisher_data %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(institution == "Minnesota") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=8) %>%  -->
<!--   ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top8colors, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(y="Count of Data DOIs", title = "Minnesota Top 8 Data Publishers") + -->
<!--     coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- #### Virginia Tech -->

<!-- ```{r, echo=FALSE} -->
<!-- by_publisher_data %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(institution == "Virginia Tech") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=8) %>%  -->
<!--   ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top8colors, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(y="Count of Data DOIs", title = "Virginia Tech Top 8 Data Publishers") + -->
<!--     coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- #### Wash U -->

<!-- ```{r, echo=FALSE} -->
<!-- by_publisher_data %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(institution == "Washington U") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=8) %>%  -->
<!--   ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top8colors, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(y="Count of Data DOIs", title = "Washington U Top 8 Data Publishers") + -->
<!--     coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- ### Top publishers - Software DOIs -->

<!-- Look at the top software publishers (This excludes CrossRef affiliation data, as software is not a resource type).  -->

<!-- ```{r} -->
<!-- by_publisher_software %>%  -->
<!--   group_by(publisher) %>%  -->
<!--   summarize(count=sum(count)) %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   mutate(pubrank = order(count, decreasing = T)) %>%  -->
<!--   ggplot(aes(x=pubrank, y=count)) + -->
<!--   geom_bar(stat="identity") + -->
<!--   scale_x_continuous(limits = c(0,20), n.breaks = 20) + -->
<!--   labs(x = "Publisher Rank", y="Number of DOIs", title="Number of Software DOIs by top Publishers")+ -->
<!--   coord_cartesian(xlim = c(1,20)) + -->
<!--   theme_bw()  -->
<!-- ``` -->

<!-- It looks like there is one primary software publisher, but we could also take the top 4 or 5 capture the majority.  -->

<!-- ```{r} -->
<!-- top6pubs_soft <- by_publisher_software_table$publisher[1:6] -->

<!-- top6colors_soft <- c("Zenodo" = "darkorange1", -->
<!--                      "Code Ocean" = "darkblue", -->
<!--                      "Institutional Repository" = "lightblue", -->
<!--                      "Optica Publishing Group" = "red",  -->
<!--                      "CoMSES Net" = "pink",  -->
<!--                      "figshare" = "purple") -->


<!-- (by_publisher_software_plot <-  by_publisher_software %>%  -->
<!--     filter(publisher %in% top6pubs_soft) %>%  -->
<!--     ggplot(aes(x=institution, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top6colors_soft, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(x = "Institution", y="Count of Software DOIs") + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5)) -->


<!-- ggsave(by_publisher_software_plot, filename = "figures/Counts of Software DOIs by Institution.png", device = "png",  width = 8, height = 6, units="in") -->

<!-- ``` -->

<!-- ### Institutional Graphs - Software {.tabset .tabset-fade .tabset-pills} -->


<!-- #### Cornell -->

<!-- ```{r ,echo=FALSE} -->
<!-- by_publisher_software %>%  -->
<!--    ungroup() %>%  -->
<!--   filter(institution == "Cornell") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=6) %>%  -->
<!--     ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top6colors_soft, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(x = "Institution", y="Count of Software DOIs", title = "Cornell Software DOIs") + -->
<!--    coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->


<!-- ``` -->

<!-- #### Duke -->

<!-- ```{r ,echo=FALSE} -->
<!-- by_publisher_software %>%  -->
<!--    ungroup() %>%  -->
<!--   filter(institution == "Duke") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=6) %>%  -->
<!--     ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top6colors_soft, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(x = "Institution", y="Count of Software DOIs", title = "DUke Software DOIs") + -->
<!--    coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- #### Michigan -->
<!-- ```{r ,echo=FALSE} -->
<!-- by_publisher_software %>%  -->
<!--    ungroup() %>%  -->
<!--   filter(institution == "Michigan") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=6) %>%  -->
<!--     ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top6colors_soft, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(x = "Institution", y="Count of Software DOIs", title = "Michigan Software DOIs") + -->
<!--    coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->


<!-- ``` -->

<!-- #### Minnesota -->

<!-- ```{r ,echo=FALSE} -->
<!-- by_publisher_software %>%  -->
<!--    ungroup() %>%  -->
<!--   filter(institution == "Minnesota") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=6) %>%  -->
<!--     ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top6colors_soft, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(x = "Institution", y="Count of Software DOIs", title = "Minnesota Software DOIs") + -->
<!--    coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->
<!-- ``` -->

<!-- #### Virginia Tech -->

<!-- ```{r ,echo=FALSE} -->
<!-- by_publisher_software %>%  -->
<!--    ungroup() %>%  -->
<!--   filter(institution == "Virginia Tech") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=6) %>%  -->
<!--     ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top6colors_soft, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(x = "Institution", y="Count of Software DOIs", title = "Virginia Tech Software DOIs") + -->
<!--    coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->


<!-- ``` -->

<!-- #### Wash U -->

<!-- ```{r ,echo=FALSE} -->
<!-- by_publisher_software %>%  -->
<!--    ungroup() %>%  -->
<!--   filter(institution == "Washington U") %>%  -->
<!--   arrange(desc(count)) %>%  -->
<!--   slice_head(n=6) %>%  -->
<!--     ggplot(aes(x=publisher, y=count, fill=publisher)) + -->
<!--     geom_bar(stat="identity", position=position_dodge(preserve = "single")) + -->
<!--     scale_fill_manual(values = top6colors_soft, name="Publisher")+ -->
<!--     guides(fill = guide_legend(title.position = "top")) + -->
<!--     labs(x = "Institution", y="Count of Software DOIs", title = "Washington U Software DOIs") + -->
<!--    coord_flip() + -->
<!--     theme_bw() + -->
<!--     theme(legend.position = "bottom", legend.title.align = .5) -->


<!-- ``` -->
